An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-28 draft.tex
Some more small changes

We aimed to learn if the proposed solution can be an efficient solution to
improve the scalability and performance of population-based optimization
algorithms. Hence, in this section, we verify the following:

\begin{itemize}
 \item If we can improve the execution time of the algorithm by adding populations
 and serverless functions to the system. In particular, what is the effect of
 these changes on the scalability of the system?

\item Having a multi-population enabled platform, with heterogeneous populations and
the support for mixing search strategies, can increase the performance of the
search by needing fewer function evaluations than a homogeneous setting?

@@

% Did you release this also with a free license? Point to
           % the URL - JJ

Next, we show the parameters for each algorithm, in Table \ref{tab:GAparams} for
the GA and in Table \ref{tab:PSOparams} for PSO. We obtained these parameters
following the same method as in a previous work \cite{garcia2017benchmarking}.
To obtain the parameters, we tested first on the Rastrigin separable function
with five dimensions. After about fifteen experiments, the most challenging
targets were achieved for this particular function. We tested again with
functions one to three, and after obtaining favorable results, the PSO and GA
algorithm parameters were set. In the GA, we randomly set the mutation and
crossover probabilities to have more heterogeneous workers; in these parameters,
the range of values is specified. We did not change these parameters during the
experiments, and only the population size and number of generations were
provided as parameters.

>>>>

We aimed to learn if the proposed solution can efficiently
improve the scalability and performance of population-based optimization
algorithms. Hence, in this section, we verify the following:

\begin{itemize}
 \item Whether we can improve the execution time of the algorithm by adding populations
 and serverless functions to the system. In particular, what is the effect of
 these changes on the scalability of the system?

\item Can having a multi-population enabled platform, with heterogeneous populations and
the support for mixing search strategies,  increase the performance of the
search by needing fewer function evaluations than a homogeneous setting?

@@

% Maybe this should be mentioned earlier, in the workflow? - JJ

Next, we show the parameters for each algorithm, with Table \ref{tab:GAparams} for
the GA and Table \ref{tab:PSOparams} for PSO. We obtained these parameters
following the same method as in a previous work \cite{garcia2017benchmarking}.
To obtain the parameters, we tested first on the Rastrigin separable function
with five dimensions. After about fifteen experiments, the most challenging
targets were achieved for this particular function. We tested again with
functions one to three, and after obtaining favorable results, the PSO and GA
algorithm parameters were set. In the GA, we randomly set the mutation and
crossover probabilities to have more heterogeneous workers; in these parameters,
the range of values is specified. We did not change these parameters during the
experiments, and only the population size and number of generations were
provided as parameters.
